The Spatial Distribution of Local Group Satellites in a Cosmological Context

### 2016-06-12 paper/ms.tex
updated tex
cosmic web description

\begin{document}
%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Satellite Alignments in Galaxy Pairs}
\author{
  Ver\'onica Arias \thanks{v.arias@uniandes.edu.co}$^{1}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}

@@

\begin{abstract}
Alineaciones.
\end{abstract}

@@

\section{Illustris simulation}

\section{Sample Selection}

@@

@@

>>>>

\begin{document}
%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{The Spatial Distribution of Local Group Satellites in a
  Cosmological Context}  
\author{
  Ver\'onica Arias \thanks{v.arias@uniandes.edu.co}$^{1}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}

@@

\begin{abstract}
We focus on the spatial distribution of bright ($M_V<-8$) satellites and
pairs of galaxies with similar masses, isolation and kinematic
configurations as the Local Group. 
\end{abstract}

@@

\subsection{Previous studies of Local Group satellites}

@@

\section{Numerical Setup}

\subsection{Illustris simulation}

\subsection{Sample Selection}

@@

\subsection{Cosmic Web environment}

We place the pairs in our sample into the cosmic web as quantified by
the deformation tensor.
\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
This method computes a cartesian grid the tensor $T_{ij}$,
\begin{equation}
T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j}
\end{equation}
%
where $\phi$ is a pseudo-gravitational potential that follows the
Poisson equation $\nabla^2\phi=-\delta$ and the $r_i$ coordinates
correspond to a cartesian system with $i=1,2,3$.

This tensor is and symmetric and can be diagonalized.
Its eigenvalues ($\lambda_1 > \lambda_2 > \lambda_3$) and
corresponding eigenvectors ($\hat{e}_1$, $\hat{e}_2$, $\hat{e}_3$)
define the degree and direction of stability around the neighborhood
where the tensor was computed. 
This allows the classification of that region either as a peak,
filaments, sheets and voids in the case of three, two, one or zero
eigenvalues larger than a given threshold $\lambda_{th}$.

In this study we compute these eigenvalues and eigenvectors over the
dark matter component of the Illustris-3 simulation on a cubic mesh of
$74$ cells on a side. 
This resolution corresponds to $\sim 1$ Mpc h.
We interpolate the DM density on that mesh using a Cloud-In-Cell (CIC)
scheme. 
We proceed to smooth the density field with a gaussian window with a
physical scale equal to the cell size.

We choose this interpolation and smoothing scale for two reasons.
First, because it corresponds to the typical pair separation in our
sample.
Second, because it allows a direct comparison with other results in
the literature that used the same methodology to quantify the cosmic
web environment for Local Group pairs in a cosmological context
\citep{ForeroRomero2013,2015ApJ...799...45F}.
